Supplement

### 2023-05-22 paper/supplement.Rmd
poking at tau squared

```{r, include=F, echo=F}
# library(Replicate)
# do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
#   if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
#     return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
#   }
#   return(NA)
# }
# 
# do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
#   if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
#     yio=target_ES
#     vio=target_SE**2
#     yir=rep_ES
#     vir=rep_SE**2
#     t2=.21
#     pooled.SE = sqrt(vio + vir + t2)
#     PILo.sens = yio - qnorm(0.975) * pooled.SE
#     PIHi.sens = yio + qnorm(0.975) * pooled.SE
#     PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
#     return(PIinside.sens)
#   }
#   return(NA)
# }
# do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
#   if(!is.na(target_ES)&!is.na(rep_ES)){
#     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
#   }
#   return(NA)
# }
# 
# do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
#   if(!is.na(target_ES)&!is.na(rep_ES)){
#     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21, rep_SE**2))
#   }
#   return(NA)
# }
# check_sens <- d |> filter(include=="stats") |> 
#   mutate(sens_target_d=target_d_calc,
#          sens_target_se=target_SE*target_d_calc/target_ES,
#          sens_target_se2=4/target_N+target_d_calc**2/(2*target_N),
#          sens_rep_d=rep_d_calc,
#          sens_rep_se=rep_SE*rep_d_calc/rep_ES,
#          sens_target_se2=4/replication_N+rep_d_calc**2/(2*replication_N)) |> 
#   
#   rowwise() |> 
#   mutate(predInt2 = do_pred_int(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
#          p_orig2 = do_p_orig(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
#          predIntSens=do_pred_int_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
#          p_origSens=do_p_orig_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se))
# 
# 
# check_sens |> select(starts_with("sens"))
# check_sens |> #select(predInt, predInt2, predIntSens, p_orig, p_orig2, p_origSens) |> 
#   filter(signif(p_orig,2)!=signif(p_orig2,2)) |> View()
# 
# check_sens |> group_by(predIntSens) |> tally()
# check_sens |> group_by(predInt2) |> tally()
# check_sens |> group_by(predInt) |> tally()
# 
# check_sens |> ungroup() |> summarize(m=median(p_origSens))
# check_sens |> ungroup() |> summarize(m=median(p_orig2))
# check_sens |> ungroup() |> summarize(m=median(p_orig))
# 
# 
# check_sens |> mutate(r1=sens_target_d/target_ES, r2=sens_target_se/target_SE, r3=sens_rep_d/rep_ES, r4=sens_rep_se/rep_SE) |> select(r1,r2,r3,r4)
# 
# d |> select(replication_raw_stat, target_raw_stat, include, sensitivity) |> View()
```

>>>>

```{r, include=F, echo=F}
library(Replicate)
do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
  }
  return(NA)
}

do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
    yio=target_ES
    vio=target_SE**2
    yir=rep_ES
    vir=rep_SE**2
    t2=.21**2
    pooled.SE = sqrt(vio + vir + t2)
    PILo.sens = yio - qnorm(0.975) * pooled.SE
    PIHi.sens = yio + qnorm(0.975) * pooled.SE
    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
    return(PIinside.sens)
  }
  return(NA)
}
do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)){
    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
  }
  return(NA)
}

do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)){
    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21**2, rep_SE**2))
  }
  return(NA)
}
check_sens <- d |> filter(include=="stats") |>
  mutate(sens_target_d=target_d_calc,
         sens_target_se=target_SE*target_d_calc/target_ES,
         sens_target_se2=4/target_N+target_d_calc**2/(2*target_N),
         sens_rep_d=rep_d_calc,
         sens_rep_se=rep_SE*rep_d_calc/rep_ES,
         sens_target_se2=4/replication_N+rep_d_calc**2/(2*replication_N)) |>

  rowwise() |>
  mutate(predInt2 = do_pred_int(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
         p_orig2 = do_p_orig(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
         predIntSens=do_pred_int_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
         p_origSens=do_p_orig_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se))

check_sens |> select(starts_with("sens"))
check_sens |> #select(predInt, predInt2, predIntSens, p_orig, p_orig2, p_origSens) |>
  filter(signif(p_orig,2)!=signif(p_orig2,2)) |> View()

check_sens |> group_by(predIntSens) |> tally()
check_sens |> group_by(predInt2) |> tally()
check_sens |> group_by(predInt) |> tally()

check_sens |> ungroup() |> summarize(m=median(p_origSens))
check_sens |> ungroup() |> summarize(m=median(p_orig2))
check_sens |> ungroup() |> summarize(m=median(p_orig))

check_sens |> mutate(r1=sens_target_d/target_ES, r2=sens_target_se/target_SE, r3=sens_rep_d/rep_ES, r4=sens_rep_se/rep_SE) |> select(r1,r2,r3,r4)

d |> select(replication_raw_stat, target_raw_stat, include, sensitivity) |> View()
```
